### 2018-12-20 Vortrag/slides/sections/ddplus.tex
More notes and nicer use case sections.

\subsection{The dd+ algorithm}
\begin{frame}{The dd+ algorithm}
	\begin{center}
		Solves it all!
	\end{center}
\end{frame}

>>>>

\subsection{The dd+ algorithm}

\newcommand{\ddp}{$dd^{+}$}

\begin{frame}{The \ddp\ algorithm}
	Zeller's \textbf{extended} $dd$ algorithm \ddp\ deals with the following cases:
	\begin{enumerate}
		\item ``found (in $c_i$)'' \only<2->{$\Rightarrow$ continue search in $c_i$}
		\item ``interference'' \only<3->{$\Rightarrow$ search in $c_i$ while leaving $\bar{c_i}$ applied and vice versa}
		\item ``preference'' \only<4->{$\Rightarrow$ search in $c_i$ while leaving $\bar{c_i}$ applied}
		\item ``try again'' \only<5->{$\Rightarrow$ repeat search on same change set with twice as many subsets}
		%\item ``nothing left		
	\end{enumerate}
\end{frame}

\begin{frame}{The \ddp\ algorithm}
	Properties of \ddp:
	\begin{itemize}
		\item \ddp finds a minimal failure-inducing subset of changes as long as the changes are safe, i.e. combined they result in a consistent configuration.
		\item \ddp has at most linear time complexity like $dd$.
	\end{itemize}
\end{frame}
